I’m an agile evangalist, who have promoted DevOps for a couple of years working at two large banks in the cph area.  

I missed the coding and thus I switched back; first at Verisure and now on my own open source project. After seeing the drawbacks of MVC+Jquery/Bootstrap architecture I am dedicated of persuing learning react.JS/redux and ES6 by studying a nanodegree at Udacity. 

I am passionate about working with the mind-set of cross-functional teams introducing for example Agile processes and Tools, challenging the team to think out-side of the companies’ processes to create a better value-chain and end-to-end thinking. 

My experience of fifteen years ranges from Research (INRIA), Finance (IKANO, Nordea), Telecom (Telenor, Tre), Retail (IKEA IT), Public services (Länsstyrelsen) and Security Industry (Verisure). Focus has been on developing large systems, architecture and processes in a large range of roles spanning from developer to scrum master. For example @ Tre I was responsible for the integration platform - EAI (the main hub of integration. @ IKANO, I optimized the work process for deployment and the communication between the business and IT, which has resulted in both improved quality and decreased resources used. 

I am driven, engaged and used to handle complex discussions to find technical solutions with stakeholders from several IT-departments by using a goal and root-cause analysis approach. 


\newline\textbf{Objective:}
My goal is to work in a creative innovation-intensive R&D environment, where I can combine my passion for new technology with my drive to collaborate and improve the way of working,  with co-workers to develop software that makes a positive impact on society.
\newline
Looking forward to hearing from you!
\makeletterclosing